Deciding to Disclose

### 2015-09-26 Conclusion.tex
Pronouns

In reality it might be anticipated that midwives would not withhold judgement, and would pass on concerns about specific women to their colleagues, or that particularly dramatic stories would persist and be passed. This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared and more sophisticated model of information flow in general. This also highlights an advantage of the \ac{BACCO} approach (which we describe in section \ref{sub:sensitivity}), in diagnosing issues with model design by giving insight into parameters which are contributing inappropriately to variance in output. Coupled with the ability of emulators to rapidly explore parameter space, this clearly suggests that statistical emulation is a powerful tool to support simulation based approaches.
This is not without caveats however, since as noted in section \ref{sub:sa_results} the emulators here are indicative, but not definitive. Amongst the reasons this may arise are heteroskedasticity associated with social learning, the stochastic nature of the simulation, and a lack of precision. The latter could be improved through iterative fitting procedures, where the simulation is sampled more heavily in plausible regions of parameter space, a procedure not possible here given the dearth of data. The former issues could be addressed by a more comprehensive approach to setting the nugget, which explicitly incorporates point variance.

>>>>

In reality it might be anticipated that midwives would not withhold judgement, and would pass on concerns about specific women to their colleagues, or that particularly dramatic stories would persist and be passed. This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared and more sophisticated model of information flow in general. This also highlights an advantage of the \ac{BACCO} approach (which we describe in section \ref{sub:sensitivity}), in diagnosing issues with model design by giving insight into parameters which are contributing inappropriately to variance in output. Coupled with the ability of emulators to rapidly explore parameter space, this clearly suggests that statistical emulation is a powerful tool to support simulation based approaches.
As noted in section \ref{sub:sa_results} the emulators here are indicative, but not definitive. Amongst the reasons discrepancy arises here are heteroskedasticity associated with social learning, the stochastic nature of the simulation, and a lack of precision given the large parameter range. The former issues could be addressed by a more comprehensive approach to setting the nugget, which explicitly incorporates point variance.  The latter could be improved through iterative fitting procedures, where the simulation is sampled more heavily in plausible regions of parameter space, a procedure not possible here given the dearth of data to evaluate plausibility. That the discrepancy exists is not prohibitive in this instance, since we are not using the emulator for prediction, only to achieve a broad strokes picture of the behaviour of the simulator.

### 2015-09-26 model_description.tex
Pronouns

A game, in the game theoretic sense, can be any interaction where the result for one person is dependent on the actions of another. In this scenario, the result for the woman would seem dependent on whether the midwife chooses to refer them for specialist support (although naturally the reality can only be thought of in terms of risk mitigation), and conversely, the right choice for the midwife is somewhat contingent on what the woman is willing to tell them.

@@

This simple game is however not very informative, and clearly neglects much of the nuance of the scenario. The wider difficulty here is that the real outcome depends on an attribute of one of the players, rather than their moves. In this case, we would expect the right choices to depend on the alcohol consumption of the woman, rather than entirely on what they have claimed about it.
To reflect this, we would need different variations on the same game to reflect this attribute.

To resolve this, we can do exactly that, and cast it as a signalling game (fig \ref{fig:less_simple}), with three types of player, corresponding to categories of drinking behaviour (light, moderate, and heavy). Each of these types of player, will play a different game. This also introduces a third player, who we will call nature. Nature takes the first move, and decides the type of the woman according to some probability distribution; in this case we will allow the probability of types to be uniform. 
This changes the dynamics of play substantially, since the midwife can no longer be certain of which game they are playing, and hence which move yields the best outcome. We must also amend the moves, and payoffs slightly. The woman now claims to be one of the types, and may send a signal to say, for example, that they are a heavy drinker. We will also modify the common payoffs to allow light drinkers to get the best outcome no matter what, and moderate and heavy types to get the best outcome only if referred. We can also differentiate between the consequences of not getting help for these types by letting heavy drinkers have a very negative outcome, and moderate drinkers a slight one.

>>>>

A game, in the game theoretic sense, can be any interaction where the result for one person is dependent on the actions of another. In this scenario, the result for the woman would seem dependent on whether the midwife chooses to refer her for specialist support (although naturally the reality can only be thought of in terms of risk mitigation), and conversely, the right choice for the midwife is somewhat contingent on what the woman is willing to tell them.

@@

This simple game is however not very informative, and clearly neglects much of the nuance of the scenario. The wider difficulty here is that the real outcome depends on an attribute of one of the players, rather than their moves. In this case, we would expect the right choices to depend on the alcohol consumption of the woman, rather than entirely on what she has claimed about it.
To reflect this, we would need different variations on the same game to reflect this attribute.

To resolve this, we can do exactly that, and cast it as a signalling game (fig \ref{fig:less_simple}), with three types of player, corresponding to categories of drinking behaviour (light, moderate, and heavy). Each of these types of player, will play a different game. This also introduces a third player, who we will call nature. Nature takes the first move, and decides the type of the woman according to some probability distribution; in this case we will allow the probability of types to be uniform. 
This changes the dynamics of play substantially, since the midwife can no longer be certain of which game they are playing, and hence which move yields the best outcome. We must also amend the moves, and payoffs slightly. The woman now claims to be one of the types, and may send a signal to say, for example, that she a heavy drinker. We will also modify the common payoffs to allow light drinkers to get the best outcome no matter what, and moderate and heavy types to get the best outcome only if referred. We can also differentiate between the consequences of not getting help for these types by letting heavy drinkers have a very negative outcome, and moderate drinkers a slight one.

### 2015-09-26 simulation_schedule.tex
Pronouns

\begin{enumerate}
\item Generate 1000 women, and place them in a queue
\item Generate 100 midwives.
\item For each round of the game
\begin{enumerate}
	\item Take 100 women from the queue
	\item Pair each one with a random midwife
	\item For each pair
	\begin{enumerate}
		\item The woman sends a signal
		\item The midwife refers or not based on the signal
		\item The woman is informed of their payoff, the midwife's type, and whether they are referred
		\item The woman updates her beliefs
		\item The midwife stores the game in their memory
		\item If the woman is referred
		\begin{enumerate}
			\item The midwife is informed of the woman's true type
			\item The midwife retrospectively updates their beliefs using the true type, and memories of any games with this woman
			\item The midwife is now eligible to share their memories of games with this woman
		\end{enumerate}
	\end{enumerate}
	\item Women who have not been referred or had their baby, join the back of the queue
	\item New women are generated to replace those referred, or delivered
	\item The new women are added to the back of the queue
	\item For each referred or birthed woman
	\begin{enumerate}
		\item With probability p, their memory of games is shared with the active women
		\item They are removed from simulation
	\end{enumerate}
	\item The active women update their beliefs
	\item For each midwife with information to share
	\begin{enumerate}
		\item With probability p, their memory of games with the referred woman is shared
		\item The memory is no longer eligible to be shared
	\end{enumerate}
	\item The midwives update their beliefs
\end{enumerate}
\end{enumerate}

>>>>

\begin{enumerate}
\item Generate 1000 women, and place them in a queue
\item Generate 100 midwives.
\item For each round of the game
\begin{enumerate}
	\item Take 100 women from the queue
	\item Pair each one with a random midwife
	\item For each pair
	\begin{enumerate}
		\item The woman sends a signal
		\item The midwife refers or not based on the signal
		\item The woman is informed of her payoff, the midwife's type, and whether she is referred
		\item The woman updates her beliefs
		\item The midwife stores the game in their memory
		\item If the woman is referred
		\begin{enumerate}
			\item The midwife is informed of the woman's true type
			\item The midwife retrospectively updates their beliefs using the true type, and memories of any games with this woman
			\item The midwife is now eligible to share their memories of games with this woman
		\end{enumerate}
	\end{enumerate}
	\item Women who have not been referred or had their baby, join the back of the queue
	\item New women are generated to replace those referred, or delivered
	\item The new women are added to the back of the queue
	\item For each referred or birthed woman
	\begin{enumerate}
		\item With probability p, her memory of games is shared with the active women
		\item She is removed from simulation
	\end{enumerate}
	\item The active women update their beliefs
	\item For each midwife with information to share
	\begin{enumerate}
		\item With probability p, their memory of games with the referred woman is shared
		\item The memory is no longer eligible to be shared
	\end{enumerate}
	\item The midwives update their beliefs
\end{enumerate}
\end{enumerate}
